---
title: "S16844 - CC Analysis"
author: "Kavinda Uthsuka"
date: "9/6/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install libraries
```{r}
#install.packages("tidyverse")
#install.packages("ggplot2")
#install.packages("ggplot2")
#install.packages("GGally")
#install.packages("CCA")
#install.packages("CCP")
#install.packages("candisc")
#install.packages("skimr")
library(tidyverse)
library(ggplot2)
library(GGally)
library(CCA)
library(CCP)
library(candisc)
library(skimr)
```




Import dataset
```{r}
fat <- read.csv("Fat_Supply_Quantity_Data.csv",header = TRUE)
head(fat)
```
summary of "fat" dataset
```{r}
skim(fat)
```
set NA values to zero
```{r}
fat[is.na(fat)] <- 0
```

standardized the dataset
```{r}
st_fat <- apply(fat,2,scale)
```

Splits the varibales into two sets. First set is "Animal Resources"(ani_res) and second set is "Vegetative Resources"(veg_res).
```{r}
ani_res <- st_fat[,c('AnimalProducts','AnimalFats','Eggs','FishSeafood','Meat','Milk')]
veg_res <- st_fat[,c('Cereals','Fruits','Oilcrops','Pulses','Spices','Treenuts','VegetalProducts','VegetableOils','Vegetables')]
```

Correlation between two sets
```{r}
matcor(ani_res,veg_res)
```
Canonical correlation model
```{r}
cc_model <- cc(ani_res,veg_res)
```

Canonical correlations
```{r}
cc_model$cor
```

Test the significance of canonical correlations
```{r}
rho <- cc_model$cor
n <- dim(ani_res)[1]
p <- dim(ani_res)[2]
q <- dim(veg_res)[2]

#Wilk's test
p.asym(rho,n,p,q,tstat = "Wilks")
```

Lawley-Hotelling test
```{r}
p.asym(rho,n,p,q,tstat = "Hotelling")
```

Pillai's test
```{r}
p.asym(rho,n,p,q,tstat = "Pillai")
```

Roy's largest root test
```{r}
p.asym(rho,n,p,q,tstat = "Roy")
```

Test the independence between two sets of variables
```{r}
Wilks(cancor(ani_res,veg_res))
```

Significant canonical correlations
```{r}
cc_model$cor[1:4]
```
Squared canoncal correlations
```{r}
cc_model$cor[1:4]^2
```


Canonical coefficients of "ani_res"/"X" set
```{r}
cc_model$xcoef
```

Canonical coefficeints of "veg_res"/"Y" set
```{r}
cc_model$ycoef
```
Canonical loadings
```{r}
loadings <- comput(ani_res,veg_res,cc_model)
```

Correlation between "ani_res" variables and the canonical variables for "ani_res"
```{r}
loadings$corr.X.xscores
```

Correlations between "veg_res" variables and the canonical variables for "veg_res"
```{r}
loadings$corr.Y.yscores
```

Correlation between the "ani_res" variables and the canonical variate for "veg_res"
```{r}
loadings$corr.X.yscores
```

Correlation between the "veg_res" variables and the canonical variate for "ani_res"
```{r}
loadings$corr.Y.xscores
```

















